Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-07-07 analysis/paper/paper.Rmd
Update paper with input from Nancy

Trays of NSIC Rc222, a short-season inbred irrigated lowland rice variety with 114 day maturity when transplanted were established on 19 December 2014. Trays were randomised and transplanted using a mechanical transplanter on 9 January 2015.

@@

Nurseries of NSIC Rc222 were established on 7 January 2016 experiments. Seedlings were transplanted by hand 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20 cm within and between rows.

@@

@@

fig.2_cap <- figure_nums(name = "fig_2", 
                        caption = "Sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years. Five different nitrogen treatments were applied to split plots depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180). Points represent the mean of four replications.")

@@

fig.4_cap <- figure_nums(name = "fig_4", 
                        caption = "Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points. Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS). Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS. Five different nitrogen treatments were applied to split plots depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")

fig.5_cap <- figure_nums(name = "fig_5", 
                        caption = "Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and nitrogen rate (NRTE) on sheath blight tiller incidence, tiller severity and leaf severity. Five different nitrogen treatments were applied to split plots depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")

@@

##### Estimates plot
`r figure_nums("fig_5")`
```{r fig_5, fig.cap="fig.5_cap"}

@@

plot_estimates_paper(models[[1]], main_title = "2015")
mtext(text = "Tiller Incidence", side = 2, line = 6)
mtext(text = "a", side = 3, line = 0, adj = 1, cex = 0.75)

plot_estimates_paper(models[[2]])
mtext(text = "Tiller Severity", side = 2, line = 6)
mtext(text = "c", side = 3, line = 0, adj = 1, cex = 0.75)

plot_estimates_paper(models[[3]], main_title = "2016")
mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)

plot_estimates_paper(models[[4]])
mtext(text = "d", side = 3, line = 0, adj = 1, cex = 0.75)

>>>>

Trays of NSIC Rc222 were seeded on 19 December 2014. NSIC Rc222 is an inbred variety released by the Philippine Rice Research Institute (PhilRice), with a 114 day maturity when transplanted were established. The variety is commonly grown by farmers in the area, having moderate resistance to brown plant hopper, green leaf hopper and yellow stem borer, but susceptibility to tungro. Plots were established by manually transplanting seedlings on 9 January 2015 in hills with six to eight seedlings per hill and a distance of 20cm within and between rows.

@@

Nurseries of NSIC Rc222 were established on 7 January 2016 experiments. Seedlings were transplanted by hand from 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20 cm within and between rows.

@@

The correlations between tiller sheath ShB incidence and tiller and leaf ShB severity were tested using Spearman’s correlation test, `cor.test`, [@R2018]. No correlation was found, so the analysis was completed for each variable independently with no assumed interaction.

@@

fig.2_cap <- figure_nums(name = "fig_2", 
                        caption = "Sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years. Five different N treatments were applied to split plots depending on the experiment. In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180). Points represent the mean of four replications.")

@@

fig.4_cap <- figure_nums(name = "fig_4", 
                        caption = "Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points. Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS). Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS. Five different N treatments were applied to split plots depending on the experiment. In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")

fig.5_cap <- figure_nums(name = "fig_5", 
                        caption = "Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on sheath blight tiller incidence and tiller severity. Five different N treatments were applied to split plots depending on the experiment. In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")

fig.6_cap <- figure_nums(name = "fig_6", 
                        caption = "Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) and the interaction of the two treatments on sheath blight leaf severity. Five different N treatments were applied to split plots depending on the experiment. In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")
```

@@

##### Tiller estimates plots

`r figure_nums("fig_5")`
```{r fig_5, fig.cap="fig.5_cap"}

@@

plot_tiller_estimates_paper(models[[1]], main_title = "2015")
mtext(text = "Tiller Incidence", side = 2, line = 6)
mtext(text = "a", side = 3, line = 0, adj = 1, cex = 0.75)

plot_tiller_estimates_paper(models[[2]])
mtext(text = "Tiller Severity", side = 2, line = 6)
mtext(text = "c", side = 3, line = 0, adj = 1, cex = 0.75)

plot_tiller_estimates_paper(models[[4]], main_title = "2016")
mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)

plot_tiller_estimates_paper(models[[5]])
mtext(text = "d", side = 3, line = 0, adj = 1, cex = 0.75)

##### Leaf estimates plots

`r figure_nums("fig_6")`
```{r fig_6, fig.cap="fig.5_cap"}

par(mfcol = c(1, 2))

plot_tiller_estimates_paper(models[[3]], main_title = "2015")
mtext(text = "Leaf Severity", side = 2, line = 6)
mtext(text = "a", side = 3, line = 0, adj = 1, cex = 0.75)

plot_tiller_estimates_paper(models[[6]], main_title = "2016")
mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)
